\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-10-29 R/create_figures.Rmd
trying to get paper to knit
but it depends on a lot of things, not working yet

```{r prepare_data, message=FALSE, warning=FALSE}
# read NEON domain polygons
neon_domains <- sf::st_read("data/shp/NEON_Domains.shp", quiet = TRUE)

# read spectral data
all_spectra <- readr::read_csv(here::here("data","cleaned_spectra.csv"))
spectra_locations <- all_spectra %>%  
  # grab the latitude and longitude coordinates for each spectrum 
  select(latitude = adjDecimalLatitude, longitude = adjDecimalLongitude) %>% 
  # remove redundant rows
  distinct() %>%
  # convert each to a SF point with geographic coordinates 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

@@

```{r}
ggsave(filename = here::here("output", "study_area.pdf"),
       width = 12, height = 8)
```

>>>>

```{r prepare_data, message=FALSE, warning=FALSE}

# download and unzip NEON domain data
url <- "https://www.neonscience.org/sites/default/files/NEONDomains_0.zip" 
dest_dir <- here::here("analysis", "data", "shp_data")
if(!dir.exists(dest_dir)){
  dir.create(dest_dir)
}
dest_file <- here::here("analysis", "data", "shp_data", "NEONDomains.zip")
download.file(url, dest_file)
unzip(dest_file, exdir = dest_dir)

# read NEON domain polygons
neon_domains <- sf::st_read(here::here("analysis", "data", "shp_data", "NEON_Domains.shp"), 
                            quiet = TRUE)

# read spectral data
cleaned_spectra <- readr::read_csv(here::here("analysis", "data", "derived_data", 
                                              "cleaned_spectra.csv"))
spectra_locations <- cleaned_spectra %>%  
  # grab the latitude and longitude coordinates for each spectrum 
  select(latitude = adjDecimalLatitude, longitude = adjDecimalLongitude) %>% 
  # remove redundant rows
  distinct() %>%
  # convert each to a SF point with geographic coordinates 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326)

@@

```{r}
message("saving study area figure...")
ggsave(filename = here::here("analysis", "figures", "study_area.pdf"),
       width = 12, height = 8)
```

### 2020-10-29 analysis/paper/paper.Rmd
trying to get paper to knit
but it depends on a lot of things, not working yet

# Methods {-}
NEON data collection protocols
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
Packages neonUtilities, geoNEON, neonhs (cite)

@@

```{r spectra, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```

@@

```{r excel, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

@@

>>>>

# Methods {-}
NEON data collection protocols
AOP flights
Plant mapping 
Network of sites and observations (how many? ecoclimatic domains? ecosystem coverage?
Figure \@ref(fig:fig_studyArea)

@@

Extracted hyperspectral data for all mapped stems at NEON sites
Figure \@ref(fig:fig_spectraExtracted)
Assumed plant locations don't change over time 
Filtered plants to keep only "live" ones
NEON data products (cite)
Spectrometer orthorectified surface directional reflectance mosaic
Woody plant vegetation structure field based measurements
Mask created for water absorption bands (cite)
Packages neonUtilities, geoNEON, neonhs (cite)

@@

```{r fig_studyArea, fig.cap = "Map of the NEON sampling locations and domains with data that we used in this study.", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "study_area.pdf"))
```

@@

```{r fig_honestWork, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
knitr::include_graphics(here::here("analysis", "figures", "honest_work.jpeg"))
```

@@

## Figure 3 {-}

```{r fig_spectraExtracted, fig.cap = "", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis", "figures", "spectra_figure_test.png"))
```
